---
title: "rtutorial3"
output: html_document
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
data("trees")
head(trees)
```

Q1. Create a histogram showing the distribution of Girth.
```{r}
ggplot(data = trees,
       aes(x = Girth)) +
  geom_histogram(bins = 20, color = "forestgreen", fill = "lightgreen") +
  labs(
    title = "Distribution of Girth",
    x = "Girth",
    y = "Frequency"
  )

```

Q2. Create a histogram showing the distribution of Volume.

```{r}
ggplot(data = trees,
       aes(x = Volume)) +
  geom_histogram(bins = 20, color = "forestgreen", fill = "lightgreen") +
  labs(
    title = "Distribution of Volume",
    x = "Volume",
    y = "Frequency"
  )

```

Q3. Create a scatterplot showing the relationship between Girth and Volume.

```{r}
ggplot(data= trees,
       aes(x = Girth, y = Volume)) +
  geom_point() +
  labs(
    x = "Girth",
    y = "Volume"
  )
```

Q4. Use the Shapiro–Wilk test to assess whether Volume is normally distributed. Report the p-value and state whether the data are normally distributed.

```{r}
shapiro.test(trees$Volume)
```
P-value = 0.003579 
El p value es < 0.05 asi que se concluye que no esta distribuido normalmente


Q5. Repeat the Shapiro–Wilk test for Girth. Report the p-value and state whether Girth is normally distributed.

```{r}
shapiro.test(trees$Girth)
```
p-value = 0.08893
El p value es >0.05 asi que se concluye que si sigue una distribucion normal





